---
title: "HW2"
author: "Georgia Warren"
date: "9/25/2021"
output: html_document
---

# Question 1  

How many flights have a missing `dep_time`? What other variables are missing? What might these rows represent?  

```{r}
library(nycflights13)
library(dplyr)
library(ggplot2)

# Counting flights by missing `dep_time`
flights %>% 
  filter(is.na(dep_time)) %>% 
  summarise(mising_dep_time = n())

# Checking which variables contain NAs
summary(flights)  

# Flights by missing `dep_time` in which other variables are also missing
flights %>% 
  filter(is.na(dep_time)) %>%
  select(dep_time, dep_delay, arr_time, arr_delay, air_time)
```

These rows might represent flights that have been canceled. 

  
# Question 2  
  
Currently `dep_time` and `sched_dep_time` are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
flights %>% 
  mutate(dep_time_min = dep_time %/% 100 * 60 + dep_time %% 100,
         sched_dep_time_min = sched_dep_time %/% 100 * 60 + sched_dep_time %% 100) %>% 
  select(dep_time_min, sched_dep_time_min)
```

# Question 3  
  
Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with `ggplot(aes(x= ,y=)) + geom_point()`.

```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(cancelled_per_day = sum(),
            n = n(),
            mean_dep_delay = mean(dep_delay,na.rm=TRUE),
            mean_arr_delay = mean(arr_delay,na.rm=TRUE)) %>% 
  ggplot(aes(x = cancelled_per_day, y = avg_delay)) + geom_point()



flights %>%
  mutate(dep_date = lubridate::make_datetime(year, month, day)) %>%
  group_by(dep_date) %>%
  summarise(cancelled = sum(is.na(dep_delay)), 
            n = n()),
            mean_dep_delay = mean(dep_delay,na.rm=TRUE),
            mean_arr_delay = mean(arr_delay,na.rm=TRUE)) %>%
    ggplot(aes(x= cancelled/n)) + 
    geom_point(aes(y=mean_dep_delay), colour='blue', alpha=0.5) + 
    geom_point(aes(y=mean_arr_delay), colour='red', alpha=0.5) + 
    ylab('mean delay (minutes)')
```

