---
title: "HW2"
author: "Georgia Warren"
date: "9/25/2021"
output: html_document
---

Link to github: https://github.com/gewarrren/gewarrren.git

# Question 1  

How many flights have a missing `dep_time`? What other variables are missing? What might these rows represent?  

```{r}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(lubridate)

# Counting flights by missing `dep_time`
flights %>% 
  filter(is.na(dep_time)) %>% 
  summarise(mising_dep_time = n())

# Checking which variables contain NAs
summary(flights)  

# Flights by missing `dep_time` in which other variables are also missing
flights %>% 
  filter(is.na(dep_time)) %>%
  select(dep_time, dep_delay, arr_time, arr_delay, air_time)
```

These rows might represent flights that have been canceled. 

  
# Question 2  
  
Currently `dep_time` and `sched_dep_time` are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
flights %>% 
  mutate(dep_time_min = (dep_time %/% 100) * 60 + (dep_time %% 100),
         sched_dep_time_min = (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100)) %>% 
  select(dep_time_min, sched_dep_time_min)
```

# Question 3  
  
Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with `ggplot(aes(x= ,y=)) + geom_point()`.

```{r}

flights %>%
  mutate(dep_day = make_datetime(year, month, day))  %>%
  group_by(dep_day) %>%
  summarise(canceled = sum(is.na(dep_delay)), 
            count = n(),
            mean_dep_delay = mean(dep_delay, na.rm=TRUE),
            mean_arr_delay = mean(arr_delay, na.rm=TRUE)) %>%
  ggplot(aes(x = canceled/count)) +
           geom_point(aes(y=mean_dep_delay, color = "dep_delay"), alpha =0.35) + 
           geom_point(aes(y=mean_arr_delay, color = "arr_delay"), alpha =0.35) +
           xlab('canceled flights per day') +
           ylab('mean delay (minutes)')

```
  
Most of the canceled flights remain around 0 for a range of delay times, besides a few exceptions.  

